Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-23 compact_boson.tex
[draft] todo added to App.G

We recall that the gluing condition is written as
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}_{t=0^-}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix}_{t=0^+}
\end{aligned}\end{equation}
where the derivatives are evaluated at the appropriate limit. In this appendix, we shall take the definition $x^\pm=x\pm t$ and $\partial_\pm=\partial_x\pm\partial_t$. Therefore we establish the scattering matrix as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
%The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x \phi^2$ term changes sign, we therefore have 
%\begin{equation}
%\begin{aligned}
%\label{eq:def_S_in_app_2}
%\begin{pmatrix}
%\partial_+\phi^1\\
%\partial_+\phi^2
%\end{pmatrix}
%=S(\theta)
%\begin{pmatrix}
%\partial_-\phi^1\\
%\partial_-\phi^2
%\end{pmatrix}
%\end{aligned}
%\end{equation}
%Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
%\begin{equation}
%\begin{aligned}
%\label{eq:def_S_in_app_2}
%\sum_{n\in\mathbb{Z}}
%\begin{pmatrix}
%\bar{a}_n^1\bar{z}^{-n}\\
%\bar{a}_n^2\bar{z}^{-n}
%\end{pmatrix}
%=S(\theta)
%\sum_{n\in\mathbb{Z}}
%\begin{pmatrix}
%a_n^1{z}^{-n}\\
%a_n^2{z}^{-n}
%\end{pmatrix}
%\end{aligned}
%\end{equation}
%As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
%\begin{equation}\begin{aligned}
%a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
%\end{aligned}\end{equation}
%The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}. 
The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_+\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_-\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
a_n^2z^{-n}
\end{pmatrix}
=-S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
\end{aligned}
\end{equation}
As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
\begin{equation}\begin{aligned}
a^i_n-(-S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{equation}
The solution of the $n \neq 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}, with an extra minus sign. Following our boundary state calculation in the main text, it is clear that this extra minus sign, which is the result of {\bf T}-duality, does not affect our conclusion.

>>>>

We recall that the gluing condition is written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\begin{pmatrix}
\partial_+\phi^1\\
-\partial_+\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
-\partial_-\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
For convenience, we shift $\phi^2\rightarrow-\phi^2$ by a sign. This amounts to reparameterize the S-matrix and exchange the two sectors of $O(2)$ group. But this will not change our conclusion in the main text. 
\todo[inline]{Check the parameterization} 
Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
=S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}
\end{aligned}
\end{equation}
As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
\begin{equation}\begin{aligned}
a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

%We recall that the gluing condition can written as
%\begin{equation}\begin{aligned}
%\label{eq:def_M}
%\begin{pmatrix}
%\partial_t\phi^1\\
%\partial_x\phi^1
%\end{pmatrix}_{t=0^-}
%=M\begin{pmatrix}
%\partial_t\phi^2\\
%\partial_x\phi^2
%\end{pmatrix}_{t=0^+}
%\end{aligned}\end{equation}
%where the derivatives are evaluated at the appropriate limit. In this appendix, we shall take the definition $x^\pm=x\pm t$ and $\partial_\pm=\partial_x\pm\partial_t$. Therefore we establish the scattering matrix as
%\begin{equation}
%\begin{aligned}
%\label{eq:def_S_in_app}
%\begin{pmatrix}
%\partial_+\phi^1\\
%\partial_-\phi^2
%\end{pmatrix}
%=S(\theta)
%\begin{pmatrix}
%\partial_-\phi^1\\
%\partial_+\phi^2
%\end{pmatrix}
%\end{aligned}
%\end{equation}
%
%The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
%\begin{equation}
%\begin{aligned}
%\label{eq:def_S_in_app_2}
%\begin{pmatrix}
%\partial_+\phi^1\\
%\partial_+\phi^2
%\end{pmatrix}
%=S(\theta)
%\begin{pmatrix}
%\partial_-\phi^1\\
%\partial_-\phi^2
%\end{pmatrix}
%\end{aligned}
%\end{equation}
%We note that the parameterization of S-matrix is \emph{different} from Eq.~\eqref{eq:def_S}, but this will not change our conclusions in the main text. Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
%\begin{equation}
%\begin{aligned}
%\label{eq:def_S_in_app_2}
%\sum_{n\in\mathbb{Z}}
%\begin{pmatrix}
%\bar{a}_n^1\bar{z}^{-n}\\
%\bar{a}_n^2\bar{z}^{-n}
%\end{pmatrix}
%=-S(\theta)
%\sum_{n\in\mathbb{Z}}
%\begin{pmatrix}
%a_n^1{z}^{-n}\\
%a_n^2{z}^{-n}
%\end{pmatrix}
%\end{aligned}
%\end{equation}
%\todo[inline]{Check the sign and parameterization of S}
%As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
%\begin{equation}\begin{aligned}
%a^i_n-(-S^{-1}_{ij})\bar{a}^j_{-n}=0
%\end{aligned}\end{equation}
%The solution of the $n \neq 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}, with an extra minus sign. Following our boundary state calculation in the main text, it is clear that this extra minus sign, which is the result of {\bf T}-duality, does not affect our conclusion.
